---
title: "Homework4_bootstrap"
author: "Peter Byrd"
date: "October 13, 2016"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 4 - Bootstrap code

This is the bootstrap code for Homework 4.  It includes the code for 4 samples, two random normal samples of 50 and 100, and two random exponential samples of 50 and 100.

# Normal sample with sample size of 50

```{r}
# Normal distribution with sample size = 50
#
samp <-50          # sample size
iter <-1000        # number of iterations to run
x <- rnorm(samp,10,2)
xbar <- mean(x)
x_sd <- sd(x)
# Initialize variables
bootnorm <- numeric(iter)
bootsd <- numeric(iter)
# Run iterations and build vector with mean and sd of each sample
for (i in 1:iter) {
  bootsamp <- sample(x,size=samp,replace=TRUE)
  bootnorm[i] <- mean(bootsamp)
  bootsd[i] <- sd(bootsamp)
}
# Report results of original sample versus all bootstrap samples
xbar            # Original Mean
x_sd            # Original Standard Deviation
mean(bootnorm)  # Average of sample Mean
mean(bootsd)    # Average of sample Standard Deviation
```

# Histogram of the bootnorm data with the sample size of 50.

```{r echo=FALSE}
# Show histogram of distribution of means that approximate normal distribution
hist(bootnorm,col="red",main=c("bootnorm w/sample size of ",samp))
#
# End of normal distribution with sample size = 50
```

You can see that the bootnorm sample has a relatively normal distribution, thus supporting the central limit theorem.


# Normal sample with sample size of 100

```{r}
# Normal distribution with sample size = 100
samp <-100         # sample size
iter <-1000        # number of iterations to run
x <- rnorm(samp,10,2)
xbar <- mean(x)
x_sd <- sd(x)
# Initialize variables
bootnorm <- numeric(iter)
bootsd <- numeric(iter)
# Run iterations and build vector with mean and sd of each sample
for (i in 1:iter) {
  bootsamp <- sample(x,size=samp,replace=TRUE)
  bootnorm[i] <- mean(bootsamp)
  bootsd[i] <- sd(bootsamp)
}
# Report results of original sample versus all bootstrap samples
xbar            # Original Mean
x_sd            # Original Standard Deviation
mean(bootnorm)  # Average of sample Mean
mean(bootsd)    # Average of sample Standard Deviation
```

# Histogram of the bootnorm data with the sample size of 100.

```{r echo=FALSE}
# Show histogram of distribution of means that approximate normal distribution
hist(bootnorm,col="red",main=c("bootnorm w/sample size of ",samp))
#
# End of normal distribution with sample size = 100
```

You can see that the bootnorm sample has a relatively normal distribution, thus supporting the central limit theorem.

# Exponential sample with sample size of 50

```{r}
# Exponential distribution with sample size = 50
#
samp <-50          # sample size
iter <-1000        # number of iterations to run
x <- rexp(samp,10)
xbar <- mean(x)
x_sd <- sd(x)
# Initialize variables
bootexp <- numeric(iter)
bootsd <- numeric(iter)
# Run iterations and build vector with mean and sd of each sample
for (i in 1:iter) {
  bootsamp <- sample(x,size=samp,replace=TRUE)
  bootexp[i] <- mean(bootsamp)
  bootsd[i] <- sd(bootsamp)
}
# Report results of original sample versus all bootstrap samples
xbar            # Original Mean
x_sd            # Original Standard Deviation
mean(bootexp)   # Average of sample Mean
mean(bootsd)    # Average of sample Standard Deviation
```

# Histogram of the bootexp data with the sample size of 50.

```{r echo=FALSE}
# Show histogram of distribution of means that approximate normal distribution
hist(bootexp,col="red",main=c("bootexp w/sample size of ",samp))
#
# End of exponential distribution with sample size = 50
```

You can see that the bootexp sample has a relatively normal distribution, thus supporting the central limit theorem.


# Exponential sample with sample size of 100

```{r}
# Exponential distribution with sample size = 100
#
samp <-100         # sample size
iter <-1000        # number of iterations to run
x <- rexp(samp,10)
xbar <- mean(x)
x_sd <- sd(x)
# Initialize variables
bootexp <- numeric(iter)
bootsd <- numeric(iter)
# Run iterations and build vector with mean and sd of each sample
for (i in 1:iter) {
  bootsamp <- sample(x,size=samp,replace=TRUE)
  bootexp[i] <- mean(bootsamp)
  bootsd[i] <- sd(bootsamp)
}
# Report results of original sample versus all bootstrap samples
xbar            # Original Mean
x_sd            # Original Standard Deviation
mean(bootexp)  # Average of sample Mean
mean(bootsd)    # Average of sample Standard Deviation
```

# Histogram of the bootexp data with the sample size of 100.

```{r echo=FALSE}
# Show histogram of distribution of means that approximate normal distribution
hist(bootexp,col="red",main=c("bootexp w/sample size of ",samp))
#
# End of exponential distribution with sample size = 100
```

You can see that the bootexp sample has a relatively normal distribution, thus supporting the central limit theorem.

# End of homework
